The imprint of global magma oceans on exoplanet demographics

### 2023-04-09 src/tex/ms.tex
Section 6.1

\subsection{Statistical imprint of exoplanet climates}
We showed in Sect.~\ref{sec:res_signature} that injecting the theoretically predicted radius inflation effect into a synthetic planet population following the currently known demographics leaves a distinct pattern in the radius and density distribution as a function of instellation.
Such a statistical imprints of the runaway greenhouse transition was suggested before~\citep{Turbet2019}, and our simulations show quantitatively how the contributions of the individual radius changes combine to create a significant demographic signal.
Its strength depends on largely unknown factors such as the planetary volatile content, but turned out to be well in the detectable range under reasonable assumptions of these factors.

Our finding that the expected trend is strong except for extremely low water mass fractions gives reason for optimism regarding its detection.
It also presents a potential for constraints on the water inventory of terrestrial planets in the case of a non-detection.
Such constraints will shed light on whether the initial water content is variable~\citep{Lichtenberg2019} or there is a predominant quantity.
Ultimately, such measurements will shed light on the question of if planets like Earth received their water from primordial sources during their formation or if it was supplied later~\citep[e.g.,][]{Raymond2004}.
%Should a successful detection occur, the time dependencies discussed above should be taken into account when using this population-level information to constrain exoplanet climates.
%Measuring these impacts would indeed provide the first empirical evidence of the habitable zone concept.
Overall, searching for the runaway greenhouse discontinuity appears to be the most promising approach toward a first empirical test of the habitable zone concept.

>>>>

\subsection{Statistical imprint of exoplanet climates}
We showed in Sect.~\ref{sec:res_signature} that injecting the theoretically predicted radius inflation effect into a synthetic planet population following the currently known demographics leaves a distinct pattern in the radius and density distribution as a function of instellation.
The transit radius inflation was suggested before as an observational diagnostic to probe the runaway greenhouse transition~\citep{Turbet2019}, and our simulations show quantitatively how the contributions of the individual radius changes combine to create a significant demographic signal.
Its strength depends on largely unknown factors such as the planetary volatile content, but turned out to be well in the detectable range under reasonable assumptions of these factors.

Our finding that the expected trend is strong except for extremely low water mass fractions gives reason for optimism regarding its detection.
It also presents a potential for constraints on the water inventory of terrestrial planets in the case of a non-detection.
Such constraints will shed light on whether the initial water content of rocky planetary is bifurcated by systematic inter-system effects~\citep{Lichtenberg2019,2021ApJ...913L..20L,2022ApJ...938L...3L} or if there is a predominant volatile-enrichment across planetary systems that is only modified by intra-system effects, such as migration \citep{Schlecker2021} and escape \citep{Owen2016}.
Ultimately, such measurements will shed light on the question of if planets like Earth received their water from primordial sources during their formation or if it was supplied later~\citep[e.g.,][]{Raymond2004}.
%Should a successful detection occur, the time dependencies discussed above should be taken into account when using this population-level information to constrain exoplanet climates.
%Measuring these impacts would indeed provide the first empirical evidence of the habitable zone concept.
Overall, searching for the runaway greenhouse discontinuity appears to be the most promising approach toward a first empirical test of the habitable zone concept.
